% !TeX root = thesis.tex
\documentclass{master_thesis}
\addbibresource{refs.bib}

\begin{document}

\section{Background}

\subfile{2accessibility.tex}

\subsection{Component libraries}

\todo{ start from design systems \citep{Churchill2019}}

Component Driven Development (CDD) is a development methodology that anchors the build process around components \citep{Coleman2017}. In \citeyear{Coleman2017} \citeauthor{Coleman2017} called CDD the biggest trend in user interface (UI) development.

A component is a well-defined and independent piece of UI, like a button, checkbox or card \citep{Ella2019}. This approach correlates well with other similar widespread principles that promote modularity in software development like atomic design and micro-front-ends. Designing each component as a standalone unit improves maintenance, reusability, and testing, shortens the learning curve and makes development faster.

The key to success here is the separation of concerns and isolating a logical piece so that it can be worked without distractions. It promotes concentrating on details and refining the element as much as possible. These pieces can be combined into more complex components if needed and when combined they can make up views that become the whole site or web page.

It is not very straightforward to preview one single separated component and if you need to set up a test or live environment for the whole webpage it would defeat the purpose of dividing the big problem into manageable chunks. In development tools called component explorers are often used to mitigate that.

Component Explorer is a separate application that showcases the components in various states \citep{Coleman2017}. Working on a single component by manipulating the entire web page or app to a certain state can be difficult without a tool like that. This allows developers to test a given component in all the states that have been defined in isolation and make it easy to build one component at a time. It also makes it easier to go through all the possible states in one component and promotes the reusability of these elements.

Bit, Storybook and Styleguidist are popular tools used in component library development \citep{Ella2019}. Bit lets you pack the bundled and encapsulated components and share them on the cloud where your team can visually explore them. Storybook supports multiple frameworks and provides a rapid component development and test environment. The environment also allows you to present and document your library for better reusability. Styleguidist is useful for documentation and demoing different components.

Design Systems are a popular way to help companies scale design work and build products with consistent user experience \citep{Yew2020}. \citeauthor{Yew2020} defines it as: "...a repository of reusable components that follow a set of shared design principles". Many companies build their own Design System. It should include a component library, style guide, design and content guidelines, design token library, interactive prototyping tools and accessibility guidelines.

Many big companies have a design system with an open source code that includes a component library, making it possible to reuse and extend them. Some of the more known ones include Material-UI \citep{MUS}, Adobe Spectrum \citep{Adobe} and Bootstrap \citep{Collings}.

% These all work together to help keep things consistent across multiple projects by providing small building blocks that can be used to create complex designs.  It can be built with HTML or by using a framework like React or Vue.

% Component libraries are a part of the company's Design System.  Design systems include values and principles along, with branding, guidelines and all the building blocks and design patterns to create a successful product or service. It governs the design process in the organization. A component library or UI kit, UI library, and UI component library are one of the building blocks of a design system.


Using a component library provides consistency and better quality. These components can be polished over time to provide the best user experience to end users when they are integrated into the final product. The effort that can be put into developing a component that will be used in multiple projects is bigger than what would be reasonable for a single use case.

\end{document}
